---
output: github_document
---

```{r include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mapthai
An R package storing the ligtweight geospatial polygon data of Thailand administrative level 1-3 including province (Changwat), district (Amphoe) and subdistrict (Tambon) in geojson and rda (`sf` class) format. Please see more details in [package website](https://piyayut-ch.github.io/mapthai/)

**Notes:**  
- Thailand maps are downloaded from [UNOCHA](https://data.humdata.org/dataset/thailand-administrative-boundaries)  
- Source: Royal Thai Survey Department update 6 November 2019   
- Maps are simplified using [mapshaper](https://mapshaper.org)  
  * Import Options : detect line intersections  
  * Simplification menu : check prevent shape removal  
  * Method : Visvalingam / effective area  


# แผนที่ไทย
R package ที่มีไฟล์แผนที่ขนาดเล็กของไทย เหมาะสำหรับการทำ data visualization มีไฟล์ทั้ง 
geojson และ rda (ในรูปแบบ class `sf`) โดยแผนที่ไทยมี 3 ระดับ ได้แก่ จังหวัด อำเภอ และตำบล
ดูรายละเอียดเพิ่มเติมได้ที่ [package website](https://piyayut-ch.github.io/mapthai/)

**หมายเหตุ:**  
- แผนที่ไทยโหลดมาจาก [UNOCHA](https://data.humdata.org/dataset/thailand-administrative-boundaries)  
- แหล่งข้อมูล: กรมแผนที่ทหาร เมื่อวันที่ 6 พ.ย. 2562  
- ลดขนาดของแผนที่ (simplify) ด้วย webtool ที่ชื่อ [mapshaper](https://mapshaper.org)  
  โดยเลือกปรับแต่งค่าต่าง ๆ ดังนี้  
  * Import Options : detect line intersections  
  * Simplification menu : check prevent shape removal  
  * Method : Visvalingam / effective area  


## Installation

You can install the released version of mapthai from [github repo](https://github.com/piyayut-ch/mapthai) with:

``` r
# remotes::install_github("piyayut-ch/mapthai")
```

## Example

### 1. Plot map using plot method of `sf` class
```{r example, dpi=200}
library(mapthai)
library(sf)

# basic example code
plot(tha2[, c('adm2_pcode', 'adm1_pcode')]) 
```

### 2. Plot interactive plot using leaflet
```{r, eval = FALSE}
library(leaflet)
leaflet(tha2) %>%
  addProviderTiles(providers$CartoDB) %>%
  addPolygons(color = "grey", weight = 1)
```

### 3. Reference table
```{r}
library(dplyr)
library(gt)

ref_tha %>%
  head()
```

```{r}
ref_tha %>% 
  filter(adm2_pcode == "TH1015")
```

### 4. Join `sf` object with data and plot
```{r, dpi=200}
tha1 %>%
  left_join(rice_2562, by = c("adm1_th" = "location")) %>%
  select(production, area_plant, yield_plant) %>%
  plot()
```